Evaluating `Graphical Perception' with CNNs

### 2018-03-31 PAPER/00_introduction.tex
Updates from ShareLaTeX

Convolutional neural networks (CNNs) have been successfully applied to a wide range of visual tasks, most famously to natural image object recognition~\cite{krizhevsky_imagenet2012, simonyan_very_deep2014, szegedy2015}, for which some claim equivalent or better than human performance. This performance comparison is often motivated by the idea that CNNs model or reproduce the early layers of the visual cortex, even though they do not incorporate many details of biological neural networks or model higher-level abstract or symbolic reasoning~\cite{yamins2016using, hassabis2017neuroscience, human_vs_machine_vision}. While CNN techniques were originally inspired by neuroscientific discoveries, recent advances in processing larger datasets with deeper networks have been the direct results of engineering efforts. Throughout this significant advancement, researchers have aimed to understand why and how CNNs produce such high performance~\cite{goodfellow_book, deeplearning_blackbox2017}, with recent works targeting the systematic evaluation of the visual perception limits of CNNs~\cite{clevr, not_so_clevr}.

One fundamental application of human vision is to understand data visualizations. This is a task unlike processing natural images, where real-world objects and their effects are abstracted into data and represented with visual marks. As a field, visualization catalogues and evaluates human perception of these marks, such as in the seminal \emph{graphical perception} experiments of Cleveland and McGill~\cite{cleveland_mcgill}. This work describes nine elementary perceptual reasoning tasks, such as position relative to a scale, length, angle, area, and shading density, plus orders their reasoning difficulty. But, with increasing research interest in the machine analysis of graphs, charts, and visual encodings, it seems pertinent to question whether CNNs are able to process these basic graphical elements and derive useful measurements from the building blocks of information visualization.

As such, we reproduce Cleveland and McGill's human perceptual experiments with CNNs, and discuss to what extent they have `graphical perception'. To perform this evaluation, we parametrize the elementary perceptual tasks and experiments suggested by Cleveland and McGill~\cite{cleveland_mcgill}, and define a set of regression tasks to estimate continuous variables. Against human perception, we pit four neural networks: a three-layer multilayer perceptron (MLP), the LeNet 2-layer CNN~\cite{lenet}, the VGG 19-layer CNN~\cite{simonyan_very_deep2014}, and the Xception 36-layer CNN~\cite{xception}. As CNNs trained on natural images are said to mimic layers of the human visual cortex, we investigate whether using weights trained on natural images (via ImageNet~\cite{imagenet}) or weights trained from scratch on elementary graphical perception tasks produces more accurate measurements and greater generalization.

We test these four networks across four scenarios presented by Cleveland and McGill~\cite{cleveland_mcgill}: 1) Nine elementary perceptual tasks with increasing parameteric complexity, e.g., length estimation with fixed x, then with varying x, then with varying width, including cross-network evaluations testing the generalizability of networks to unseen parameters; 2) The position-angle experiment, which compares judgements of bar charts to pie charts, 3) The position-length experiment, which compares grouped and divided bar charts, and 4) The bars and framed rectangles experiments, where visual cues aid ratio perception. We also investigate whether our CNNs can detect a proportional change in a measurement across scales, in relation to Weber's law.

With these experiments, we describe a ranking defining the ease with which our tested CNN architectures can estimate elementary perceptual tasks, as an equivalent to Cleveland and McGill's ranking for human perception. Further, we discuss the implications of our results and derive recommendations for the use of CNNs in perceiving visualizations. We accompany this paper with open source code and our input and results data, both to enable reproduction studies and to spur new machine perception systems more adept at graphical perception: \url{http://rhoana.org/perception}

%Cleveland and McGill's work in the 1980s has led to many insights for modern information visualization research such as the identification of elementary perceptional tasks or that bar charts are easier to understand than pie charts.

%\emph{Can we leverage decades of visualization research to understand the way convolutional neural networks process data?}
%
%Information visualization has been an established research field for decades which has resulted in numerous insightful findings in regards to how human beings can best process information visually.
%Unpublished preliminary experiments have shown that data representations customized for the human eye also can improve the performance of an automatic classifier. 
%While the reasons for this are still unknown, specified research can most certainly advance the understanding of deep neural networks.
%
%\subsection{From Biological Vision to Machine Learning}
%
%%\begin{figure}[t]
%%	  \includegraphics[width=\linewidth]{biology_vs_cnn.png}
%%  \caption{The Biological Vision (schematic)}
%%	\label{fig:vision}
%%\end{figure}
%
%Biological vision is an extremely powerful system which allows humans the ability, and seemingly without effort, to recognize an enormous amount of distinct objects in the world. 
%Object detection is extremely difficult and therefore is especially impressive as light intensities can change by levels of magnitude and contrast between foreground and background is so often low. 
%In addition, the visual scene changes every time the human body or human eyes move. 
%This visual system exhibits a very noisy structure but because it is organized by layers it has inspired the mathematical theory of multilayer neural networks. 
%What is remarkable is that even though current machine learning models do not resemble the complexity of its biological pendant, they inherently generalize extremely well. 
%Neural networks trained on one specific task can be used to perform detection or segmentation of, seemingly, unrelated objects with relatively minor retraining. 
%The reported classification performance is superior to that of humans and the question in regards to their functionality opens an interesting research topic.
%
%In 1962 Hubel and Wiesel were the first to begin studying the visual cortex from the standpoint of a neuroscientist. Their experimental findings on cats and macaque monkeys suggested a hierarchy of cells with increasing complexity which was then later transferred to the hierarchical model of different layers. Twenty years later, this insight was translated to the Neocognitron quantitative model, by Fukushima and Miyake, which ultimately led to the important work of Hinton, Bengio, and LeCun in the 1980s. Their work on stochastic gradient descent approximation, and the availability of faster computer hardware then led to today’s breakthrough of deep learning networks. In the last decade, this field has exhibited rapid growth, constant evolution, and new applications in various domains.
%
%We think that the biological inspiration of modern convolutional neural networks yields the evaluation of principles of human perception with computers.
%

>>>>

Artificial intelligence has taken the world of technology by storm. Deep multilayer neural networks are being successfully applied in a wide range of applications that are regularly outperforming humans in object recognition \cite{krizhevsky_imagenet2012, simonyan_very_deep2014,szegedy2015}. 
Originally inspired by neuroscientific discoveries, the recent advances in deep learning have been the direct results of engineering efforts, more specifically in convolutional neural networks (CNNs). 
While there has been significant advancement, this does not mean we understand what CNNs are doing and we are in fact treating them as blackboxes without detracting from their success \cite{goodfellow_book, deeplearning_blackbox2017}. 
Our current knowledge of biological vision suggests that modern machine learning models indeed mimic the underlying biology by abstracting the many details of biological neural networks \cite{yamins2016using, hassabis2017neuroscience}.

Despite tremendous research efforts and generating massive datasets, we are far from fully understanding biological vision. 
Similarly, we are constantly developing inventive features for deep artificial networks without truly understanding it in its entirety. As a result, a double discrepancy is observed. 
Advances in neuroscience can revolutionize machine learning by reverse-engineering neural circuits, yielding new classifiers which, in turn, can help process the massive biological data. 
There are many existing questions which must be answered in order to fill this gap of our understanding.

\paragraph{Proposed Solution}

We focus on perception... experiments from cleveland mcgill..

\paragraph{Validation and Applications}

\paragraph{Contributions}

%\emph{Can we leverage decades of visualization research to understand the way convolutional neural networks process data?}
%
%Information visualization has been an established research field for decades which has resulted in numerous insightful findings in regards to how human beings can best process information visually.
%Unpublished preliminary experiments have shown that data representations customized for the human eye also can improve the performance of an automatic classifier. 
%While the reasons for this are still unknown, specified research can most certainly advance the understanding of deep neural networks.

\subsection{Biological Vision}

%\begin{figure}[t]
%	  \includegraphics[width=\linewidth]{biology_vs_cnn.png}
%  \caption{The Biological Vision (schematic)}
%	\label{fig:vision}
%\end{figure}

Biological vision is an extremely powerful system which allows humans the ability, and seemingly without effort, to recognize an enormous amount of distinct objects in the world. 
Object detection is extremely difficult and therefore is especially impressive as light intensities can change by levels of magnitude and contrast between foreground and background is so often low. 
In addition, the visual scene changes every time the human body or human eyes move. 
This visual system exhibits a very noisy structure but because it is organized by layers it has inspired the mathematical theory of multilayer neural networks. 
What is remarkable is that even though current machine learning models do not resemble the complexity of its biological pendant, they inherently generalize extremely well. 
Neural networks trained on one specific task can be used to perform detection or segmentation of, seemingly, unrelated objects with relatively minor retraining. 
The reported classification performance is superior to that of humans and the question in regards to their functionality opens an interesting research topic.

In 1962 Hubel and Wiesel were the first to begin studying the visual cortex from the standpoint of a neuroscientist. Their experimental findings on cats and macaque monkeys suggested a hierarchy of cells with increasing complexity which was then later transferred to the hierarchical model of different layers. Twenty years later, this insight was translated to the Neocognitron quantitative model, by Fukushima and Miyake, which ultimately led to the important work of Hinton, Bengio, and LeCun in the 1980s. Their work on stochastic gradient descent approximation, and the availability of faster computer hardware then led to today’s breakthrough of deep learning networks. In the last decade, this field has exhibited rapid growth, constant evolution, and new applications in various domains.

GOALS
\begin{itemize}
	\item reduce the gap between neurobiology and data science to advance the understanding of visual cortex inspired machine learning
	\item insights for infovis for machines
\end{itemize}

CONTRIBUTIONS
\begin{itemize}
	\item experiments of cleveland mcgill with systematic parametrization and evaluation for computational perception
	\item ranking of elementary perceptual tasks for machine perception
	\item validation of weber's law for feedforward neural networks
	\item many insights for infovis for machines
\end{itemize}

### 2018-03-31 PAPER/02_experimental_setup.tex
Updates from ShareLaTeX

We conduct quantitative experiments to measure how different convolutional neural networks perceive low-level visual encodings, such as positions, angles, curvatures, and lengths. We formulate these measurement tasks as logistic regression problems: given a stimuli image of an elementary visualization, the networks must estimate the single quantity present or the ratio between multiple quantities present.

For each experiment, we use a single factor between-subject design, with the factor being the network used. This lets us evaluate whether different network designs are competitive against existing human perception results. We train each network in a supervised fashion with a mean-squared error (MSE) loss between the ground-truth labels and the network's estimate of the measurement from observing the generated stimuli images. Then, we test each network's ability to generalize to new examples with a separate data, created using the same stimuli generator function but with unseen ground-truth measurements (Section~\ref{sec:data}).

% We define a series of hypotheses prior to each experiment.

\subsection{Networks}
\label{sec:networks}

\noindent{\textbf{Multilayer Perceptron.}} As a baseline, we use a multilayer perceptron (MLP), but without the prior convolutional layers as is typical in network designs for solving visual tasks (Fig.~\ref{fig:classifiers}). Our MLP contains a layer of $256$ perceptrons, which are activated as rectified linear units (ReLU)~(Fig.~\ref{fig:classifiers}). We train this layer with dropout (probability $= 0.5$) to prevent overfitting, and then combine these ReLU units to regress our output measurement.
\\~\\
\noindent{\textbf{Convolutional Neural Networks.}} We compare different convolutional neural networks (CNNs) with both `trained from scratch' weights and pre-trained weights on a database of natural images (1000-class ImageNet \cite{imagenet}). These networks are the traditional LeNet-5 with 2 layers, which was designed to recognize hand-written digits~\cite{lenet}; the VGG19 network with 19 layers, which was designed to solve the ImageNet object recognition challenge~\cite{simonyan_very_deep2014}; and the Xception network with 36 layers~\cite{xception}, which was also designed to solve the ImageNet object recognition challenge plus the 15,000-class JFT object recognition challenge~\cite{Hinton2015}. Each of these networks has as its last layers an MLP architecture equivalent to our baseline, and so they act as earlier image and feature processors for this final regressor. Since the networks are of different architectures, the number of trainable parameters changes, with some networks having more capacity than others (Table~\ref{tab:parameters}).

For \emph{VGG19} and \emph{Xception}, we have two variants: the network trained from scratch on elementary perceptual tasks, plus the network using weights that were previously trained on the ImageNet object recognition challenge \emph{except} for the MLP layer. This is intended to produce early-layer features which mimic human vision, and then to see whether they are more or less useful than networks trained from scratch. 
\\~\\
\noindent{\textbf{Optimization.}} All network hyperparameters, optimization methods, and stopping conditions are fixed across networks (Table \ref{tab:parameters}). We train for $1000$ epochs using stochastic gradient descent with Nesterov momentum, but stop early if the loss does not decrease for ten epochs.
\\~\\
\noindent{\textbf{Environment.}} We run all experiments on Tesla X and Tesla V100 graphical processing units. We use the KERAS framework with a TensorFlow backend to train the networks, and use the scikit-image library to generate the stimuli. % and scikit-learn libraries - JT: What do we use this for?

\begin{table}[t]
\centering
\caption{\textbf{Network Training.} We use different feature generators as input to a multilayer perceptron which performs linear regression. This results in different sets of trainable parameters. As a baseline, we also train the MLP directly on the visualization images without any additional feature generation.}
\resizebox{\linewidth}{!}{
\begin{tabular}{lrl}
%	\toprule
%	\makecell{Classifier} & \makecell{Convolutional\\Layers} & \makecell{Trainable\\Parameters} \\
%	\midrule
%	MLP & $0$ & $2,560,513$ \\
%	\emph{LeNet} + MLP & $2$ & $8,026,083$ \\
%	\emph{VGG19} + MLP & $16$ & $21,204,545$ \\
%	\emph{Xception} + MLP & $36$ & $25,580,585$ \\
%	\bottomrule
	\toprule
	Network & \makecell{Trainable\\Parameters} & Optimization \\
	\midrule
	MLP & $2,560,513$ & SGD (Nesterov momentum)\\
	\emph{LeNet} + MLP & $8,026,083$ & Learning rate: $0.0001$\\
	\emph{VGG19} + MLP & $21,204,545$ & Momentum: $0.9$ \\
	\emph{Xception} + MLP & $25,580,585$ & \makecell[tl]{Batchsize: 32\\Epochs: $1000$ (Early Stopping)}\\
	\bottomrule
\end{tabular}
}
\label{tab:parameters}
\vspace{-4mm}
\end{table}
%\begin{figure}[t]
%	\centering
%	  \includegraphics[width=\linewidth]{classifiers.pdf}
%  \caption{The multilayer perceptron (MLP) in our experiments has 256 neurons which are activated as rectified linear units (ReLU). We use Dropout regularization to prevent overfitting. We learn categorical and unordered dependent variables using the softmax function and perform linear regression for continuous variables. The MLP can learn the visualizations directly but we also learn features generated by LeNet (2 conv. layers, filter size $5\time5$), VGG19 trained on ImageNet (16 conv. layers, filter size $3\times3$), or Xception trained on ImageNet (36 conv. layers, filter size $3\times3$) to increase the number of trainable parameters.}
%	\label{fig:classifiers}
%\end{figure}
\begin{figure}[t]
	\centering

    \subfloat[Feature Generation]{
		\includegraphics[width=4.8cm,valign=c]{classifier_left.pdf}
		\vphantom{\includegraphics[width=3.5cm,valign=c]{classifier_right.pdf}}
	}
	\hfill
    \subfloat[Multilayer Perceptron]{
		\includegraphics[width=3.5cm,valign=c]{classifier_right.pdf}
	}

  \caption{\textbf{Network Architecture.} The multilayer perceptron (MLP) in our experiments has 256 neurons which are activated as rectified linear units (ReLU). We use Dropout regularization to prevent overfitting. As output, we perform linear regression for continuous variables. The MLP can learn to represent the visualizations directly, but we also learn features generated by LeNet (2 conv. layers, filter size $5\times5$), VGG19 (16 conv. layers, filter size $3\times3$), or Xception (36 conv. layers, filter size $3\times3$) to test different model complexities.}
	\label{fig:classifiers}
\end{figure}

\subsection{Data}
\label{sec:data}

\noindent\textbf{Image Stimuli and Labels.} 
We create our stimuli visualizations as 100$\times$100 binary images, rasterized without interpolation. We write a parameterized stimuli generator for each elementary task. The number of possible parameter values differs per experiment, and we summarize these in Table~\ref{tab:encoding_parameters} and Section~\ref{sec:parametrizations}. Before use, we scale the generated images into an unbiased range: images to the range of $-0.5$ to $0.5$. Then, we add subtle random noise (uniformly distributed between $0-0.05$) to each pixel to introduce variation which prevents the networks from simply `remembering' each different image.

Each stimuli image also has an associated ground truth label representing the parameter set which generated the image, e.g., the length in pixels of a bar. As before, we scale these labels to the range of $0.0$ to $1.0$, which represent the maximum and minimum values that this parameter can take.
\\~\\
\noindent\textbf{Training/Validation/Test Splits.} For each task, we use 60,000 training images, 20,000 validation images, and 20,000 test images. To create these datasets, we generate stimuli from random parameters and add them to the sets until the target number is reached, while maintaining distinct (random) parameter spaces for each set to ensure that there is no leakage between training and validation/testing.

\subsection{Measures and Analysis}

\noindent\textbf{Cross Validation.} For reproducibility, we perform repeated random sub-sampling validation, also known as Monte Carlo cross-validation, during our experiments. We run every experiment seperately twelve times, and randomly select (without replacement) the $60\%$ of our data as training data, $20\%$ as validation, and $20\%$ as test. 
%Our large data sample size of 100,000 guarantees that every single observation of our parameterizations will be selected at least once (excluding noise patterns). -> JT: No it doesn't.
% Finally, we average the results over the runs. -> JT: Fine, but we'll do distributions anyway, so not worth saying.
\\~\\
\noindent{\textbf{Task Accuracy.}} In their 1984 paper, Cleveland and McGill use the midmean logistic absolute error metric (\emph{MLAE}) to measure perception accuracy. To allow comparison between their human results and our machine results, we also use MLAE as a presentation metric:
\begin{equation}
	\textnormal{MLAE} = log_2( | \textnormal{predicted percent} - \textnormal{true percent} | + .125)
\end{equation}
In addition to this metric, we also calculate standard error metrics such as the mean squared error (\emph{MSE}) and the mean absolute error (\emph{MAE}). This allows a more direct comparison of percent errors. Please note that our networks were trained using MSE loss and not directly with MLAE.
\\~\\
\noindent{\textbf{Task Confidence Intervals.}} We follow Cleveland and McGill and present $95\%$ confidence intervals. We approximate the value of the $97.5$ percentile point of the normal distribution for simplicity with $1.96$ as suggested by the central limit theorem~\cite{central_limit}.
\\~\\
\noindent{\textbf{Confirmatory Data Analysis.}} To accept or reject our hypotheses, we analyze dependent variables using analysis of variance (ANOVA) followed by parametric tests. JT: Which tests?
\\~\\
\noindent{\textbf{Training Efficiency.}} We use the training convergence rate as a measure of how easy or hard a particular task is for the network to learn to solve. This is defined as the MSE loss decrease per training epoch, which is an indicator of the training efficiency of the network with respect to the visual encoding.
\\~\\
\noindent\textbf{Network Generalizability.} We evaluate generalizability by asking a network previously trained upon one task parameterization to answer questions about the same type of task stimuli but with more complex parameterization, e.g., estimating bar length without and with changes in stroke width.

Further, some experiments compare different visual encoding types, e.g., bar plot vs.~stacked bar plot. We train and evaluate individual networks for each parameterization, plus we also train and evaluate a networks on stimuli across the different types. This single decision-making software better mimics the judgements that a human would be able to make. 
%This scenario affects the optimization process and result in networks with more flexible knowledge with the caveat of longer training times. -> JT: Save it for the results discussion.

>>>>

The experiments shown in this paper are either supervised regression or classification tasks. We formulate any estimation of quantities (e.g. angles, positions, lengths etc.) as a regression problem between $0$ and $1$. The output indicates the percentage in regards to the degrees of freedom of the individual experiment. If the experiment involves a choice, we formulate it as a classification problem.

\subsection{Measures}

\textbf{Accuracy.} We use the same metric as Cleveland and McGill to measure accuracy.
\begin{equation}
	\log_2( | \textnormal{predicted percent} - \textnormal{true percent} | + .125)
\end{equation}
\\~\\
\noindent{\textbf{Confidence Intervals.}} We follow the notion of Cleveland and McGill to compute the confidence intervals.
\\~\\
\noindent{\textbf{Efficiency.}} We use the convergence rate based on the decrease of loss per training epoch as an indicator for the efficiency of the classifier in combination with a visual encoding. For regression tasks the loss is defined as mean squared error (MSE) and for classification tasks the loss is categorical cross-entropy.

\subsection{Classifiers}

Our classifiers are built upon a multilayer perceptron (MLP) which is a feedforward artificial neural network. We combine this MLP with different convolutional neural networks (CNNs) for preprocessing and feature generation. These include the traditional LeNet trained from scratch, as well as VGG19 and Xception trained using ImageNet.
\\~\\
\noindent{\textbf{Multilayer Perceptron.}} The multilayer perceptron in this paper has $256$ neurons which are activated as rectified linear units~(Fig.~\ref{fig:classifiers}). We then add a dropout layer to prevent overfitting and compute linear regression or classification (softmax).
\\~\\
\noindent{\textbf{Convolutional Neural Networks.}} We use CNNs to generate additional features as input to the MLP. We train the \emph{LeNet} classifier with tune it specifically towards each visualization. For \emph{VGG19} and \emph{Xception}, we generate features using previously trained weights on ImageNet.
\\~\\
\noindent{\textbf{Optimization.}} All networks are optimized using stochastic gradient descent with Nesterov momentum using fixed parameters (Table \ref{tab:parameters}). We train for $1000$ epochs but stop early if the loss does not decrease for ten epochs.
\\~\\
\noindent{\textbf{Environment.}} We run all experiments on an NVIDIA DGX1 machine with Tesla V100 graphical processing units. We use the KERAS framework with tensorflow.

\begin{table}[t]
\centering
\caption{We use different feature generators as input to a multilayer perceptron which performs linear regression or the classification task. This yields different sets of trainable parameters. We also train the MLP directly on the visualizations without any additional feature generation.}
\resizebox{\linewidth}{!}{
\begin{tabular}{lrl}
%	\toprule
%	\makecell{Classifier} & \makecell{Convolutional\\Layers} & \makecell{Trainable\\Parameters} \\
%	\midrule
%	MLP & $0$ & $2,560,513$ \\
%	\emph{LeNet} + MLP & $2$ & $8,026,083$ \\
%	\emph{VGG19} + MLP & $16$ & $21,204,545$ \\
%	\emph{Xception} + MLP & $36$ & $25,580,585$ \\
%	\bottomrule
	\toprule
	Classifier & \makecell{Trainable\\Parameters} & Optimization \\
	\midrule
	MLP & $2,560,513$ & SGD (Nesterov momentum)\\
	\emph{LeNet} + MLP & $8,026,083$ & Learning rate: $0.0001$\\
	\emph{VGG19} + MLP & $21,204,545$ & Momentum: $0.9$ \\
	\emph{Xception} + MLP & $25,580,585$ & \makecell[tl]{Batchsize: 32\\Epochs: $1000$ (Early Stopping)}\\
	\bottomrule
\end{tabular}
}
\label{tab:parameters}
\vspace{-4mm}
\end{table}

\begin{figure}[t]
	\centering
	  \includegraphics[width=\linewidth]{classifiers.pdf}
  \caption{The multilayer perceptron (MLP) in our experiments has 256 neurons which are activated as rectified linear units (ReLU). We use Dropout regularization to prevent overfitting. We learn categorical and unordered dependent variables using the softmax function and perform linear regression for continuous variables. The MLP can learn the visualizations directly but we also learn features generated by LeNet (2 conv. layers, filter size $5\time5$), VGG19 trained on ImageNet (16 conv. layers, filter size $3\times3$), or Xception trained on ImageNet (36 conv. layers, filter size $3\times3$) to increase the number of trainable parameters.}
	\label{fig:classifiers}
\end{figure}

\subsection{Data}

We create all visualizations as parametrized rasterized images without interpolation. The number of parameters differs per experiment as summarized in Table~\ref{tab:encoding_parameters} and section~\ref{sec:parametrizations}. We add subtle random noise ($0.05$) to each pixel to introduce additional variation.
\\~\\
\noindent\textbf{Training/Validation/Test Splits.} We specify the size of each split set as follows: 60,000 training images, 20,000 validation images, and 20,000 test images. We then randomly add parameterized visualizations to the sets while guaranteeing that each set is disjunct from each other in terms of encoded variables. This eliminates leakage during training and evaluation. We also scale each set independently: images to the range of $-.5$ to $.5$ and labels to the range of $0.0$ to $1.0$. 
\\~\\
\noindent\textbf{Cross-classifier variability.} We also evaluate classifiers previously trained with one visualization on the same type of visualizations with different parameters by decreasing and increasing the variability of the generated images.
